%-------------------------
% Resume in Latex
% Adapted from: Sourabh Bajaj (https://github.com/sb2nov/resume)
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{newtxtext} % Palatino-based serif font
% cochineal palatino 
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubheadingExtra}[2]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, rightmargin=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.jaeyeonpark.kr}{\Large Jaeyeon Park}} &
    Email: \href{mailto:ok6530@snu.ac.kr}{ok6530@snu.ac.kr}\\ %\href{mailto:ok6530@snu.ac.kr}{jaeyeonparc@icloud.com} \\
  & \href{http://www.jaeyeonpark.kr}{www.jaeyeonpark.kr}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Seoul National University}{Seoul, Republic of Korea}
      {Ph.D. Candidate, Electrical and Computer Engineering}{2023 -- present}
      \resumeItemListStart
        \resumeItem{Lab}{Power Conversion and Systems Lab (PCSL)}
        \resumeItem{Advisor}{Prof. Shenghui Cui}
        \resumeItem{Research}{Modular multilevel converters (MMC), medium-voltage variable frequency drives,
          power-hardware-in-the-loop (PHIL) testing, real-time simulation.}
      \resumeItemListEnd

    \resumeSubheading
      {Seoul National University}{Seoul, Republic of Korea}
      {M.S., Electrical and Computer Engineering; GPA:\, 4.03/4.3}{2021 -- 2023}
      \resumeItemListStart
        \resumeItem{Lab}{Electrical Engineering \& Power Electronics Lab (EEPEL)}
        \resumeItem{Advisor}{Prof. Seung-Ki Sul}
        \resumeItem{Thesis}{Real Time Torque Control of PMSM under Flux Weakening Operation Based on Nonlinear Optimization.}
      \resumeItemListEnd

    \resumeSubheading
      {Seoul National University}{Seoul, Republic of Korea}
      {B.S., Electrical and Computer Engineering; GPA:\,3.35/4.3}{2015 -- 2021}
      \resumeItemListStart
        \resumeItem{Thesis}{Battery Electric Vehicle Motor Control System Design and Implementation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Power Conversion \& Systems Lab, Seoul National University}{Seoul, Republic of Korea}
      {Ph.D. Candidate; Advisor: Prof. Shenghui Cui}{2023 -- present}
      \resumeItemListStart
        \resumeItem{MMC-Based MV Variable Frequency Drive}
          {Led development of control algorithms and control systems for a 5\,MW Modular Multilevel Converter VFD
           for shipboard applications.}
        \resumeItem{PHIL Testing for Megawatt-Scale MMC}
          {Developed a partial power-hardware-in-the-loop framework for in-situ dynamic and
           steady-state validation of individual submodules in a megawatt-scale MMC.}
      \resumeItemListEnd

    \resumeSubheading
      {Electric Energy Processing \& Control Lab, Seoul National University}{Seoul, Republic of Korea}
      {M.S. Researcher; Advisor: Prof. Seung-Ki Sul, IEEE Fellow}{2021 -- 2023}
      \resumeItemListStart
        \resumeItem{IPMSM Optimal Control}
          {Developed online MTPA tracking and flux-weakening torque control algorithms for
           interior permanent magnet synchronous motors using sequential quadratic programming (SQP)
           and min-max optimization, achieving robust performance under parameter uncertainties without lookup tables.}
      \resumeItemListEnd

      \resumeSubheading
      {Signal Processing Systems Lab, Seoul National University}{Seoul, Republic of Korea}
      {Research Assistant; Advisor: Prof. Wonyong Sung, IEEE Fellow}{2020 -- 2021}
      \resumeItemListStart
        \resumeItem{Snoring Diagnosis Application}
          {Developed custom ESP32 board and custom firmware for snoring diagnosis.}
      \resumeItemListEnd

      \resumeSubheading
      {Republic of Korea Army}{Seoul, Republic of Korea}
      {Research Engineer}{2018 -- 2020}
      \resumeItemListStart
        \resumeItem{Parallel Computing for Signal Processing}
          {Developed parallel computing algorithms
          for massive signal processing.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{ Teaching Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Seoul National University}{Seoul, Republic of Korea}
      {Teaching Assistant, Electric Machines and Control; Instructor: Prof. Seung-Ki Sul}{Fall 2021, Fall 2023}
      \resumeItemListStart
        \resumeItem{Responsibilities}{Conducted lab sessions and tutorials; assisted students with coursework and problem sets.}
      \resumeItemListEnd
    \resumeSubheadingExtra
      {Lecturer, SNU Power Electronics Center Summer School}{Summer 2022}
      \resumeItemListStart
        \resumeItem{Responsibilities}{Delivered lectures on digital signal processor programming and embedded firmware development for power electronics applications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PUBLICATIONS-----------------
\section{Publications}

  \textbf{Journal Articles}
  \resumeSubHeadingListStart

    \item\small{
    \textbf{J.~Park}, D.-J.~Kim, S.-Y.~Lee, J.-J.~Jung, S.-K.~Sul and S.~Cui, 
    ``Partial Power-Hardware-in-the-Loop Test for In-Situ Dynamic and 
    Steady-State Validation of a Single Submodule in a Megawatt-Scale MMC," 
    in \textit{IEEE Transactions on Power Electronics}, vol. 41, no. 5, pp. 8409-8427, May 2026.
    }\vspace{-2pt}

    \item\small{
    \textbf{J.~Park} et al., 
    ``Equivalent Circuit Extraction of MI-HTS Coil Including High-Frequency 
    Region for Electromagnetic Transient Simulation With Voltage-Source Converter," 
    in \textit{IEEE Transactions on Applied Superconductivity}, vol. 35, no. 7, pp. 1-11, Oct. 2025.
    }\vspace{-2pt}

    \item\small{
      D.-J.~Kim, \textbf{J.~Park}, Y.~Hong and S.~Cui, 
      ``Fault-Tolerant Independent Pole Control Scheme of Zigzag MMC for 
      Bipolar MVDC Distribution Systems," in \textit{IEEE Transactions on Power Electronics}, vol. 41, no. 6, pp. 10324-10342, June 2026.
    }\vspace{-2pt}
    \item\small{
      J.~Maeng, J.~Ham, G.~Park, \textbf{J.~Park}, H.~Wu, J.-J.~Jung, S.~Cui,
      ``A Supercapacitor Size Minimization and Energy Management Strategy for E-STATCOM
      Connected to Weak Grid,''
      \textit{International Journal of Electrical Power \& Energy Systems}, vol.~172, Art.~no.~111174, Nov.~2025.
    }\vspace{-2pt}
    \item\small{
      Y.-W.~Kim, H.~Kim, \textbf{J.~Park}, S.-K.~Sul,
      ``On-line Minimum Loss Control Strategy of IPMSM in Torque-Controlled Application,''
      \textit{ Journal of Power Electronics}, vol.~24, p.~756, Apr.~2024.
    }\vspace{-2pt}
  \resumeSubHeadingListEnd

  \textbf{Conference Papers}
  \resumeSubHeadingListStart
    \item\small{
J.~Yun, \textbf{J.~Park}, S.~Moon, G.~De Carne and S.~Cui, 
"Resource-Efficient Real-Time Simulation of Multi-Active Bridge Converters Using 
Modular Programming," \textit{2025 IEEE Kiel PowerTech}, Kiel, Germany, 2025, pp. 1-6,
    }\vspace{-2pt}


    \item\small{
      \textbf{J.~Park}, J.~Lee, D.~Kim, S.~Lee, S.~Moon, J.~Yoo, S.~Ko, S.~Cui,
      ``MMC-Based High-Power Motor Emulator for Testing of Electrical Propulsion System,''
      \textit{2025 IEEE Electric Ship Technologies Symposium\,(ESTS)}, Alexandria, VA, USA, 2025, pp. 162-169.
    }\vspace{-2pt}


    \item\small{
      S.~Moon, \textbf{J.~Park}, D.~Kim, and S.~Cui,
      ``Generator Operation Strategy for Naval Vessels with MVDC Distribution in Combat Situations,''
      \textit{2025 IEEE Electric Ship Technologies Symposium\,(ESTS)}, Alexandria, VA, USA, 2025, pp. 162-169.
    }\vspace{-2pt}


    \item\small{
  S.~Lee, \textbf{J.~Park}, D.~Kim and S.~Cui, 
  "Optimal Nearest-Level Modulation of MVDC-MMC with Decoupled Control for Lower Phase Current Total Harmonic Distortion," \textit{2025 IEEE Energy Conversion Conference Congress and Exposition (ECCE)}, Philadelphia, PA, USA, 2025, pp. 1-5.
   }\vspace{-2pt}


    \item\small{
      G.~Park, \textbf{J.~Park}, S.~Cui, S.-K.~Sul,
      ``Nonlinear Optimization-Based Power-Voltage Control of Grid-Connected Converter in
      Weak Grid,''
      \textit{2024 IEEE Applied Power Electronics Conference and Exposition\,(APEC)}, Long Beach, CA, USA, 2024, pp. 228-233.
    }\vspace{-2pt}
    \item\small{
     \textbf{J.~Park}, H.-J.~Cho, H.~Kim, S.-K.~Sul,
      ``Online Torque Control of IPMSM for Flux Weakening Operation Using Sequential
      Quadratic Programming,''
      \textit{2023 IEEE Energy Conversion Congress and Exposition\,(ECCE)}, Nashville, TN, USA, 2023, pp.~4750--4755.
    }\vspace{-2pt}
    \item\small{
      \textbf{J.~Park}, H.-J.~Cho, J.~Yun, S.-K.~Sul,
      ``Online MTPA Tracking of IPMSM Based on Min-Max Optimization,''
      \textit{2023 11th International Conference on Power Electronics and ECCE Asia (ICPE 2023 - ECCE Asia)}, 
      Jeju Island, Korea, Republic of, 2023, pp. 199-204.
    }\vspace{-2pt}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Awards}
  \resumeSubHeadingListStart
    %   \item\small{
    %   \textbf{Recipient of the KIEE Electric Love Scholarship},  The Korean Institute of Electrical Engineers, 2021
    % }\vspace{-2pt}
    \item\small{
      \textbf{Excellence Prize in Creative Design Fair 2016}, Seoul National University, 2016
    }\vspace{-2pt}
    
  \resumeSubHeadingListEnd


% %-----------SKILLS-----------------
% \section{Technical Skills}
%   \resumeSubHeadingListStart
%     \item{
%       \textbf{Power Electronics}{: MMC design \& control, motor drives (IPMSM), grid-connected converters,
%         PHIL/HIL testing, MVDC systems}
%     }
%     \item{
%       \textbf{Control}{: MTPA/flux-weakening, disturbance observer, nonlinear optimisation (SQP, min-max),
%         capacitor voltage balancing}
%     }
%     \item{
%       \textbf{Simulation \& Firmware}{: Real-time simulation, MATLAB/Simulink, C/C++ (DSP), Python}
%     }
%     \item{
%       \textbf{Communication}{: EtherCAT (IEC 61158), industrial Ethernet}
%     }
%   \resumeSubHeadingListEnd


% %-----------PROFESSIONAL AFFILIATIONS-----------------
% \section{Professional Affiliations}
%   \resumeSubHeadingListStart
%     \resumeSubItem{IEEE}{Student Member; Power Electronics Society (PELS); Industry Applications Society (IAS)}
%   \resumeSubHeadingListEnd


% %-------------------------------------------
\end{document}
